---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
# DE.AHC
_by **John D. Gagnon**_
<br>
_University of California, San Francisco_

### Table of Contents  
**[Overview](#overview)**<br>
**[Installation](#installation)**<br>
**[Usage](#usage)**<br>
**[Session info](#session-info)**<br>
**[License](#license)**<br>

## Overview

A shinyapp-based GUI to visualize miR-15/16 differential expression data
along with AGO2 HITS-CLIP data for each gene.

## Installation

1. If you do not already have R installed, or your version is out of date, 
download and install the latest [version](https://cran.r-project.org). 


  + Optionally, install the latest version of 
[RStudio Desktop](https://www.rstudio.com/products/rstudio/#Desktop).


2. Download the package from GitHub

```{r eval = FALSE}
install.packages("devtools")
devtools::install_github("jdgagnon/DE.AHC")
```


## Usage

1. Load the package into the R session.

`library(DE.AHC)`

2. To initialize the shiny app, paste the following code in your R console 
and run it.

`runDEAHCapp()`

3. Optionally subset genes based on pathways or list specific genes.
Toggle checkbox to filter genes that contain miR-15/16 seed-matches in their
3'UTR

* Load your own differential expression data file
* File should be structured like:


```{r, echo=FALSE, fig.align='center'}
knitr::kable(
  matrix(c("Cd28", 2.4, 0.0000342, 0.0004244, 50, 48, 49, 62, 58, 60,
           rep("etc...", 10)), 
         ncol = 10, byrow = T), 
  col.names = c("Gene", "logFC", "PValue", "FDR", "WT_1", "WT_2", "WT_3", "cKO_1", "cKO_2", "cKO_3"))
```

* Load your own AGO2 HITS-CLIP data file
* File should be structured like:
  
```{r, echo=FALSE, fig.align='center'}
knitr::kable(
  matrix(c("Cd28", "3UTR", "mmu-miR-16-5p", TRUE, 2899,
           rep("etc...", 5)), 
         ncol = 5, byrow = T), 
  col.names = c("Gene", "Location", "miR", "Targetscan", "Sum"))
```

## Session info

Here is the output of `sessionInfo()` on the system on which this package was
developed:

```{r} 
sessionInfo()
```
<br><br>

## License

[GNU GPL-3.0-or-later](https://www.gnu.org/licenses/gpl.txt)
